Pillar 2 - Topic Modeling

### 2019-01-22 Pillar 2 - Topic Modeling.Rmd
ideal number of topics in LDA
LDA with 120 topics (ideal number)

## Ideal Number of Topic

```{r, eval = FALSE}
result <- FindTopicsNumber(

@@

FindTopicsNumber_plot(result1)
save(result,
     file = "LDA_ntopics.RDATA")
```

@@

```{r LDA fit, cache = TRUE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

LDA_overview_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
LDA_overview_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
LDA_overview_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))

LDA_manual_10 <- LDA(d_manual_cast, k = 10, control = list(seed = 123))
LDA_manual_17 <- LDA(d_manual_cast, k = 17, control = list(seed = 123))
LDA_manual_25 <- LDA(d_manual_cast, k = 25, control = list(seed = 123))
```

```{r LDA save models}
save(LDA_description_10, LDA_description_17, LDA_description_25,
     LDA_overview_10, LDA_overview_17, LDA_overview_25,
     LDA_manual_10, LDA_manual_17, LDA_manual_25,
     file = "LDA.RDATA")
```

@@

# Bet Distribution
LDA_description_10 %>% prepare_data_LDA_beta

# Gamma Distribution
LDA_description_10 %>% prepare_data_LDA_gamma(level = Cluster)
```

@@

### Plots
```{r LDA plot, cache = TRUE}
LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")

LDA_overview_10 %>% visualize_LDA_all_level(id_plot = "overview_k10")
LDA_overview_17 %>% visualize_LDA_all_level(id_plot = "overview_k17")
LDA_overview_25 %>% visualize_LDA_all_level(id_plot = "overview_k25")

LDA_manual_10 %>% visualize_LDA_all_level(id_plot = "manual_k10")
LDA_manual_17 %>% visualize_LDA_all_level(id_plot = "manual_k17")
LDA_manual_25 %>% visualize_LDA_all_level(id_plot = "manual_k25")
```

>>>>

## Ideal Number of Topics

```{r LDA number topics, eval = FALSE}
result <- FindTopicsNumber(

@@

save(result,
     file = "LDA_ntopics.RDATA")
```

```{r LDA number topics plot}
load("LDA_ntopics.RDATA")
FindTopicsNumber_plot(result)
```

@@

```{r LDA fit, cache = TRUE}
n_topics <- 120
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

for(level in levels){

  dataset   <- get(paste("d", level, "cast", sep = "_"))
  LDA_model <- LDA(dataset, k = n_topics, control = list(seed = 123))
  nam <- paste("LDA", level, n_topics, sep = "_")

  assign(
    x     = nam,
    value = LDA_model
  )

  list_nam <- c(list_nam, nam)

save(list = list_nam,
     file = "LDA.RDATA")
```

@@

# Bet Distribution
LDA_description_120 %>% prepare_data_LDA_beta

# Gamma Distribution
LDA_description_120 %>% prepare_data_LDA_gamma(level = Cluster)
```

@@

### Plots
```{r LDA plot, cache = TRUE}
LDA_description_120 %>% visualize_LDA_all_level(id_plot = "description_k120")

LDA_overview_120 %>% visualize_LDA_all_level(id_plot = "overview_k120")

LDA_manual_120 %>% visualize_LDA_all_level(id_plot = "manual_k120")
```
